ISYE 6740 HW 1

### 2024-08-29 msiddiqui60_HW1_report.tex
Latex update

\end{document}

>>>>

\susection{Sources}
\begin{enumerate}
\item https://www.kaggle.com/code/arushchillar/kmeans-clustering-using-different-distance-metrics
\item https://yann.lecun.com/exdb/mnist/
\item https://stackoverflow.com/questions/76246578/module-numpy-has-no-attribute-warnings
\item https://pyclustering.github.io/docs/0.8.2/html/da/d22/classpyclustering_1_1cluster_1_1kmeans_1_1kmeans.html
\item https://numpy.org/doc/stable/reference/generated/numpy.bincount.html
\end{enumerate}
\end{document}
